Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/sw-contract.tex
Minor upgrades
Answer Konrad's questions is section 4 and 5

The contract has six guarantees:
\begin{itemize}
\item \linesref{line:sw-guarantee-1}{line:sw-guarantee-3}
coincide events and assert well-formed output.\footnote{\konst{KLS}:I am confused about the ``coincide events''.}
\item \lineref{line:sw-guarantee-4} insists that a start happens with a request or one step after a request. At time zero the start must coincide
with the request; after that, the start must coincide with the request
or else is a response to a request one step earlier.  The guarantee
works with the assumption on \lineref{line:sw-assume-3} and thus does
not have to check for two requests in a row without a start, since the
assumption precludes that input behavior. The guarantee also does not
force the start to always happen, it only says that if it does happen,
it is under the defined conditions.

\item \lineref{line:sw-guarantee-5} forces the alert to sound if the start does not arrive within the one-step bound. Together with \lineref{line:sw-guarantee-4} this allows
for non-alerting and alerting behavior.
\item \lineref{line:sw-guarantee-6} guarantees that, if an alert has ever happened,
it continues to happen.
\end{itemize}
These six guarantees define the behavior of the SW component under the
three assumptions and correspond to the informal descriptions given
in \secref{sec:example}.

>>>>

\noindent The contract has six guarantees:
\begin{itemize}
\item \lineref{line:sw-guarantee-1}, \lineref{line:sw-guarantee-2}, and \lineref{line:sw-guarantee-3}.
A waypoint coincides with a update on the UAV location, a start coincides with a new waypoint, and waypoints are well-formed.
\item \lineref{line:sw-guarantee-4}. A start happens with a request or one step after a request. At time zero the start must coincide
with the request; after that, the start must coincide with the request
or else is a response to a request one step earlier.  The guarantee
works with the assumption on \lineref{line:sw-assume-3} and thus does
not have to check for two requests in a row without a start, since the
assumption precludes that input behavior. The guarantee also does not
force the start to always happen, it only says that if it does happen,
it is under the defined conditions.

\item \lineref{line:sw-guarantee-5}. The alert to sounds if the start does not arrive within the one-step bound. Together with \lineref{line:sw-guarantee-4} this allows
for non-alerting and alerting behavior.
\item \lineref{line:sw-guarantee-6}. If an alert has ever happened,
it continues to happen.
\end{itemize}
These six guarantees define the behavior of the SW component under the
three assumptions and correspond to the informal descriptions given
in \secref{sec:example}.

### 2022-03-28 paper/verification-conditions.tex
Answer Konrad's questions is section 4 and 5

The expanded property lists in \figref{fig:example-certificate} and
\figref{fig:hardened-certificate} are the results from verifying or
disproving the above verification conditions.  The additional
unexpanded results at the bottom of the figures prove
\emph{self-consistency} in the contracts.\emph{Needs a definition?}  It is not uncommon to
accidentally write contracts that are self-contradicting.  For
example, a contract may guarantee an output be two different values in
the same moment of time.  AGREE generates additional verification
conditions that prove each component contract, and the composition of
contracts, self-consistent.

>>>>

The expanded property lists in \figref{fig:example-certificate} and
\figref{fig:hardened-certificate} are the results from verifying or
disproving the above verification conditions.  The additional
unexpanded results at the bottom of the figures prove
\emph{self-consistency} in the contracts.
A contract is self-consistent if it does not guarantee two different values in the same moment of time, \ie, the contract is not self-contradicting.
AGREE generates additional verification
conditions that prove each component contract, and the composition of
contracts, self-consistent.
